\documentclass[12pt,a4paper]{article}

% ── Packages ──
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2.5cm]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[dvipsnames,svgnames,x11names]{xcolor}
\usepackage{tcolorbox}
\tcbuselibrary{skins,breakable,listings}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric}

% ── Colors ──
\definecolor{primaryblue}{HTML}{2563EB}
\definecolor{deepblue}{HTML}{1E40AF}
\definecolor{accentgreen}{HTML}{059669}
\definecolor{warmamber}{HTML}{D97706}
\definecolor{lightbg}{HTML}{F0F4FF}
\definecolor{codebg}{HTML}{F8FAFC}
\definecolor{boxborder}{HTML}{BFDBFE}
\definecolor{theorembg}{HTML}{EEF2FF}
\definecolor{examplebg}{HTML}{ECFDF5}
\definecolor{warningbg}{HTML}{FEF3C7}
\definecolor{tipbg}{HTML}{F0FDF4}

% ── Hyperref ──
\hypersetup{
  colorlinks=true, linkcolor=deepblue, citecolor=accentgreen,
  urlcolor=primaryblue, bookmarks=true, bookmarksopen=true,
  pdftitle={QQKRLS: A Complete Guide},
  pdfauthor={Dr. Merwan Roudane},
}

% ── Headers ──
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{primaryblue}{\small\textsc{QQKRLS Technical Guide}}}
\fancyhead[R]{\textcolor{primaryblue}{\small\thepage}}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{primaryblue}\leaders\hrule height \headrulewidth\hfill}}

% ── Section Formatting ──
\titleformat{\section}{\Large\bfseries\color{deepblue}}{{\color{primaryblue}\thesection}}{1em}{}[\vspace{-0.5em}\textcolor{primaryblue}{\rule{\textwidth}{0.8pt}}]
\titleformat{\subsection}{\large\bfseries\color{deepblue!80!black}}{{\color{primaryblue}\thesubsection}}{0.8em}{}
\titleformat{\subsubsection}{\normalsize\bfseries\color{deepblue!60!black}}{{\color{primaryblue}\thesubsubsection}}{0.6em}{}

% ── Tcolorbox styles ──
\newtcolorbox{definitionbox}[1][]{enhanced,breakable,colback=theorembg,colframe=primaryblue,
  title={\textbf{#1}},fonttitle=\bfseries\color{white},coltitle=white,
  colbacktitle=primaryblue,boxrule=0.8pt,arc=4pt,left=8pt,right=8pt,top=6pt,bottom=6pt}

\newtcolorbox{theorembox}[1][]{enhanced,breakable,colback=theorembg,colframe=deepblue,
  title={\textbf{#1}},fonttitle=\bfseries\color{white},coltitle=white,
  colbacktitle=deepblue,boxrule=0.8pt,arc=4pt,left=8pt,right=8pt,top=6pt,bottom=6pt}

\newtcolorbox{examplebox}[1][]{enhanced,breakable,colback=examplebg,colframe=accentgreen,
  title={\textbf{#1}},fonttitle=\bfseries\color{white},coltitle=white,
  colbacktitle=accentgreen,boxrule=0.8pt,arc=4pt,left=8pt,right=8pt,top=6pt,bottom=6pt}

\newtcolorbox{warningbox}[1][]{enhanced,breakable,colback=warningbg,colframe=warmamber,
  title={\textbf{#1}},fonttitle=\bfseries\color{white},coltitle=white,
  colbacktitle=warmamber,boxrule=0.8pt,arc=4pt,left=8pt,right=8pt,top=6pt,bottom=6pt}

\newtcolorbox{tipbox}[1][]{enhanced,breakable,colback=tipbg,colframe=accentgreen!70!black,
  title={\textbf{#1}},fonttitle=\bfseries\color{white},coltitle=white,
  colbacktitle=accentgreen!70!black,boxrule=0.8pt,arc=4pt,left=8pt,right=8pt,top=6pt,bottom=6pt}

% ── Code listing style ──
\lstdefinestyle{pythonstyle}{
  language=Python, basicstyle=\small\ttfamily,
  backgroundcolor=\color{codebg}, frame=single, rulecolor=\color{boxborder},
  keywordstyle=\bfseries\color{deepblue}, stringstyle=\color{accentgreen},
  commentstyle=\itshape\color{gray}, showstringspaces=false,
  breaklines=true, numbers=left, numberstyle=\tiny\color{gray},
  xleftmargin=1.5em, framexleftmargin=1.5em, tabsize=4, captionpos=b,
}
\lstset{style=pythonstyle}

% ── Theorems ──
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}

% ── Commands ──
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Hk}{\mathcal{H}_K}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bc}{\mathbf{c}}
\newcommand{\bK}{\mathbf{K}}
\newcommand{\bI}{\mathbf{I}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bLambda}{\boldsymbol{\Lambda}}

\begin{document}

% ── TITLE PAGE ──
\begin{titlepage}
\begin{center}
\vspace*{2cm}
{\Huge\bfseries\textcolor{deepblue}{QQKRLS}}\\[0.5cm]
{\LARGE\textcolor{primaryblue}{Quantile-on-Quantile Kernel-Based\\[0.2cm] Regularized Least Squares}}\\[1.5cm]
{\Large\textcolor{deepblue!70!black}{A Complete Technical Guide}}\\[0.3cm]
{\large\textcolor{gray}{From Zero to Expert --- For Researchers \& Practitioners}}\\[3cm]

\textcolor{primaryblue}{\rule{0.6\textwidth}{1.5pt}}\\[1cm]

{\Large \textbf{Dr.\ Merwan Roudane}}\\[0.4cm]
{\normalsize \texttt{merwanroudane920@gmail.com}}\\[0.3cm]
{\small
\textcolor{primaryblue}{\textbf{PyPI:}} \url{https://pypi.org/project/qqkrls/}\\
\textcolor{accentgreen}{\textbf{GitHub:}} \url{https://github.com/merwanroudane/qqkrls}
}\\[2cm]

{\large Version 1.1.1}\\[0.5cm]
{\normalsize \today}
\end{center}
\end{titlepage}

\tableofcontents
\newpage

% ── Include all parts ──
\input{guide_part1}
\input{guide_part2}
\input{guide_part3}

% ── Bibliography ──
\newpage
\section{References}

\begin{enumerate}[leftmargin=2em]
\item \textbf{Hainmueller, J.\ \& Hazlett, C.} (2014). Kernel Regularized Least Squares: Moving Beyond Linearity and Additivity without Sacrificing Interpretability. \textit{Political Analysis}, 22(2), 143--168. \href{https://doi.org/10.1093/pan/mpt024}{doi:10.1093/pan/mpt024}

\item \textbf{Sim, N.\ \& Zhou, H.} (2015). Oil Prices, US Stock Return, and the Dependence Between Their Quantiles. \textit{Journal of Banking \& Finance}, 55, 1--12. \href{https://doi.org/10.1016/j.jbankfin.2015.01.013}{doi:10.1016/j.jbankfin.2015.01.013}

\item \textbf{Adebayo, T.S., Ozkan, O.\ \& Eweade, B.S.} (2024). Do energy efficiency R\&D investments and ICT promote environmental sustainability in Sweden? A novel QQKRLS investigation. \textit{Journal of Cleaner Production}, 440, 140832. \href{https://doi.org/10.1016/j.jclepro.2024.140832}{doi:10.1016/j.jclepro.2024.140832}

\item \textbf{Adebayo, T.S., Meo, M.S., Eweade, B.S.\ \& Ozkan, O.} (2024). Analyzing the effects of solar energy innovations, digitalization, and economic globalization on environmental quality in the United States. \textit{Clean Technologies and Environmental Policy}, 26, 4157--4176. \href{https://doi.org/10.1007/s10098-024-02831-0}{doi:10.1007/s10098-024-02831-0}

\item \textbf{Scholkopf, B.\ \& Smola, A.J.} (2002). \textit{Learning with Kernels: Support Vector Machines, Regularization, Optimization, and Beyond}. MIT Press.

\item \textbf{Koenker, R.} (2005). \textit{Quantile Regression}. Cambridge University Press.

\item \textbf{Tikhonov, A.N.} (1963). Solution of Incorrectly Formulated Problems and the Regularization Method. \textit{Soviet Mathematics Doklady}, 4, 1035--1038.
\end{enumerate}

\end{document}
